Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-27 submission/Sze_Obesity_PeerJ_2016_Supp.Rmd
adjust so p-value show up

**Figure S1: Individual and Combined comparison of Obese and Non-Obese groups for Observed OTUs.**  For observed OTUs Baxter (P-value = `r format(round(alpha_tests.summary[which(alpha_tests.summary$dataset == 'baxter' & alpha_tests.summary$metric == 'sobs'), 'p.value'], 2), nsmall = 2)`, Goodrich (P-value = `r format(round(alpha_tests.summary[which(alpha_tests.summary$dataset == 'goodrich' & alpha_tests.summary$metric == 'sobs'), 'p.value'], 5), nsmall = 5)`), and Turnbaugh (P-value = `r format(round(alpha_tests.summary[which(alpha_tests.summary$dataset == 'turnbaugh' & alpha_tests.summary$metric == 'sobs'), 'p.value'], 2), nsmall = 2)`) studies individually were signficantly different for obese and non-obese groups.  When the data sets were combined and study effect was corrected for,  there was a significant difference between Non-Obese and Obese groups (P-value = `r format(round(alpha_composite.summary['sobs', 'composite_p'], 5), nsmall = 5)`)

**Figure S2: Individual and Combined comparison of Obese and Non-Obese groups for Evenness.**  For evenness only the Goodrich study (P-value = `r format(round(alpha_tests.summary[which(alpha_tests.summary$dataset == 'goodrich' & alpha_tests.summary$metric == 'shannoneven'), 'p.value'], 3), nsmall = 3)`)  individually was signficantly different for obese and non-obese groups.  When the data sets were combined and study effect was corrected for,  there was an overall significant difference between Non-Obese and Obese groups (P-value = `r format(round(alpha_composite.summary['sobs', 'composite_p'], 2), nsmall = 2)`)

>>>>

**Figure S1: Individual and Combined comparison of Obese and Non-Obese groups for Observed OTUs.**  For observed OTUs Baxter (P-value = `r format(round(alpha_tests.summary[which(alpha_tests.summary$dataset == 'baxter' & alpha_tests.summary$metric == 'sobs'), 'p.value'], 2), nsmall = 2)`, Goodrich (P-value = `r format(round(alpha_tests.summary[which(alpha_tests.summary$dataset == 'goodrich' & alpha_tests.summary$metric == 'sobs'), 'p.value'], 8), nsmall = 8)`), and Turnbaugh (P-value = `r format(round(alpha_tests.summary[which(alpha_tests.summary$dataset == 'turnbaugh' & alpha_tests.summary$metric == 'sobs'), 'p.value'], 2), nsmall = 2)`) studies individually were signficantly different for obese and non-obese groups.  When the data sets were combined and study effect was corrected for,  there was a significant difference between Non-Obese and Obese groups (P-value = `r format(round(alpha_composite.summary['sobs', 'composite_p'], 8), nsmall = 8)`)

**Figure S2: Individual and Combined comparison of Obese and Non-Obese groups for Evenness.**  For evenness only the Goodrich study (P-value = `r format(round(alpha_tests.summary[which(alpha_tests.summary$dataset == 'goodrich' & alpha_tests.summary$metric == 'shannoneven'), 'p.value'], 3), nsmall = 3)`)  individually was signficantly different for obese and non-obese groups.  When the data sets were combined and study effect was corrected for,  there was an overall significant difference between Non-Obese and Obese groups (P-value = `r format(round(alpha_composite.summary['shannoneven', 'composite_p'], 2), nsmall = 2)`)
